\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-14 docs/paper.tex
Abstract reviewed

\abstract{
The introduction of Internationalized Domain Names made access the web easier to non-English speakers.
However, it also opened the possibility of using homograph domain names maliciously.
We analyzed the potential impact of this type of attack, commonly referred to as IDN homograph attack.
Our approach was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
While most of them are not being used actively, they still possess a potential security risk as there are no guarantees they will remain inactive in the future.
}

>>>>

\abstract{
The introduction of Internationalized Domain Names (IDNs) made access the web easier to non-English speakers.
However, it also opened up the possibility of using homograph domain names maliciously, in what has been called IDN homograph attacks.
This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
Our approach to analyze its potential impact was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
While most of them are not being used actively, they still possess a potential security risk as there are no guarantees they will remain inactive in the future.
}
